Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (Multivariate Normal distribution)

### 2022-06-24 Manual.Rmd
update title with spelling corrections in manual

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for LogisticRegression (Multivariate Normal Distribution)"
output: github_document
---

@@

#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]

>>>>

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (Multivariate Normal distribution)"
output: github_document
---

@@

#### 2.2.1.5 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]
